Dish: Distribution-oblivious Shell Scripting

### 2019-11-22 pldi/draft.tex

% \begin{lstlisting}[language=sh, float=h, numbers=none, escapeinside={($}{$)}]
%  cat /proc/ >                            (($$p_4$$))
% \end{lstlisting}
% \begin{lstlisting}[language=sh, float=h, numbers=none, escapeinside={($}{$)}]
%  ls -l | wc -l                           (($$p_2$$))
% \end{lstlisting}
% \begin{lstlisting}[language=sh, float=h, numbers=none, escapeinside={($}{$)}]
%  cat * | wc -l > out.txt                 (($$p_3$$))
% \end{lstlisting}
% \begin{lstlisting}[language=sh, float=h, numbers=none, escapeinside={($}{$)}]
%  cat /proc/ >                            (($$p_5$$))
% \end{lstlisting}
% \begin{lstlisting}[language=sh, float=h, numbers=none, escapeinside={($}{$)}]
% { echo 1; echo 2; } > out.txt
% \end{lstlisting}

\begin{figure}[t]
\centering
\includegraphics[width=0.49\textwidth]{\detokenize{./figs/dish_overview.pdf}}
\caption{
  \textbf{\sys transformation overview.}
	\sys XYZ \todo{This is slightly cropped?}
}
\label{fig:overview}
\end{figure}

@@

>>>>

% \begin{lstlisting}[language=sh, float=h, numbers=none, escapeinside={($}{$)}]
%  cat /proc/ >                            (($$p_4$$))
% \end{lstlisting}
% \begin{lstlisting}[language=sh, float=h, numbers=none, escapeinside={($}{$)}]
%  cat /proc/ >                            (($$p_5$$))
% \end{lstlisting}
% \begin{lstlisting}[language=sh, float=h, numbers=none, escapeinside={($}{$)}]
% { echo 1; echo 2; } > out.txt
% \end{lstlisting}

\begin{figure}[t]
\centering
\includegraphics[width=0.49\textwidth]{\detokenize{./figs/dish_schematic.pdf}}
\caption{
  \textbf{\sys transformation overview.}
  Given a shell pipeline, \sys leverages command distributability to identify
  high-distributability stages, rewrite them, and orchestrate their execution.
}
\label{fig:overview}
\end{figure}

@@

\heading{Discussion}
As described earlier~\sx{bg}, shell commands change their operation based on command-line options.
These options can actually change the class in which a command belongs.
Consider two examples:
  (i) \ttt{cat} is in \sta, but with \ttt{-n} it jumps into \pur because it has to keep track of a counter;
  (ii) \ttt{comm} is in \pur, but with \ttt{/input1} it jumps into \sta---as it is now partially evaluated, it becomes stateless with respect to the second argument.
% TODO: closure?
